Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Figures of toy experiment; better late than never

@@

% \subsection{Ornstein-Uhlenbeck Process}
% The Ornstein-Uhlenbeck process is a noisy relaxation process that can be formulated as a Gaussian process with kernel of the form $k(r)=\exp(- \alpha |r|)$ \cite{Rasmussen:2006:Gaussian_Processes}. This corresponds to the particular case of the CGPCM where $h(t)=\sqrt{2 \alpha} \exp(- \alpha |t|)$.

% \subsection{RLC Series Circuit}
% Consider the voltage response $f(t)$ of a series circuit consisting of a resistance $R$, capacitance $C$, and inductance $L$ excited by current $x(t)$ with unity PSD due to thermal noise of the resistance. Application of Kirchhoff's voltage law \cite{Irwin:2010:Basic_Engineering_Circuit_Analysis} yields that
% \begin{align*}
%      L f'(t) + R f(t)+\frac{1}{C}\int^t f(t)\id{t} = x(t).
% \end{align*}
% Assume that the circuit is critically damped and that $R=2$ and $L=1$. Then $f(t)$ is of the form of \cref{eq:model} where $h(t) = t \exp(-t)$. Therefore, according to \cref{mod:cgpcm2}, it holds that $f(t) \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ where
% \begin{align*}
%     k_{f\cond h}(r) = \frac{1}{4}(1+|r|)\exp(-|r|).
% \end{align*}

% {\color{red} Experiment.}

% \subsection{Unvoiced Fricatives}
% Unvoiced fricatives are consonants produced by forcing air through a narrow constriction in the vocal tract, thereby creating a noisy, turbulant sound \cite{Taylor:2009:Text-To-Speech_Synthesis}.

\subsection{Head-Related Transfer Function}
A head-related transfer function (HRTF) is a transfer function that describes how an ear receives sound from a certain point in space.

@@

\subsection{Population Growth}

>>>>

\usepackage{color}
\definecolor{darkgreen}{rgb}{0,.5,0}
\definecolor{mycyan}{rgb}{0,.9,.9}

\usepackage{tabularx}

\usepackage{tikz}

@@

@@

\begin{figure*}[t]
    \centering
    GPCM
    \begin{tabularx}{\linewidth}{
            >{\centering}>{\hsize=.43\hsize}X  % ??
            >{\centering}>{\hsize=.2\hsize}X
            >{\centering}>{\hsize=.2\hsize}X
            >{\centering}>{\hsize=.2\hsize}X
        }
        $f\cond h$ & $h$ & $k_{f\cond h}$ & PSD of $k_{f\cond h}$
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/learning_known_kernels_causal_sample_gpcm_cropped.pdf}
    CGPCM
    \includegraphics[width=\linewidth, height=3cm]{resources/learning_known_kernels_causal_sample_cgpcm_cropped.pdf}
    \caption{Toy. Here {\color{red}red} denotes truth; {\color{darkgreen}green} denotes observations, the emperical autocorrelation, and the periodogram for respectively the function $f\cond h$, the kernel $k_{f\cond h}$, and PSD of $k_{f\cond h}$; {\color{blue}blue} denotes quantities learned through the MF approximation; and {\color{mycyan}cyan} denotes quantities learned through the SMF approximation.}
    \label{fig:toy_causal_sample}
\end{figure*}

\begin{figure*}[t]
    \centering
    GPCM
    \begin{tabularx}{\linewidth}{
            >{\centering}>{\hsize=.43\hsize}X  % ??
            >{\centering}>{\hsize=.2\hsize}X
            >{\centering}>{\hsize=.2\hsize}X
            >{\centering}>{\hsize=.2\hsize}X
        }
        $f\cond h$ & $h$ & $k_{f\cond h}$ & PSD of $k_{f\cond h}$
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/learning_known_kernels_acausal_sample_gpcm_cropped.pdf}
    CGPCM
    \includegraphics[width=\linewidth, height=3cm]{resources/learning_known_kernels_acausal_sample_cgpcm_cropped.pdf}
    \caption{Toy. Here {\color{red}red} denotes truth; {\color{darkgreen}green} denotes observations, the emperical autocorrelation, and the periodogram for respectively the function $f\cond h$, kernel $k_{f\cond h}$, and power spectral density $\log \mathcal{F}\{k_{f\cond h}\}$; {\color{blue}blue} denotes quantities learned through the MF approximation; and {\color{mycyan}cyan} denotes quantities learned through the SMF approximation.}
    \label{fig:toy_scausal_sample}
\end{figure*}

\subsection{Head-Related Transfer Function}
The head-related transfer function (HRTF) describes how the reception of sound by the ear depends on the position from which the sound originates.
